---
title: "Homework: Reproducibility and Professional Communication"
execute:
  error: true
author: "Ryan Barent"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 3)
```


# Reproducible Examples & Debugging

In the following examples, evaluate each problem using the criteria of a minimal reproducible example from [this StackOverflow post](https://stackoverflow.com/help/minimal-reproducible-example). 

Specifically, address the following things: 

1. Are the question and problem description complete?

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

3. Is the example minimal? Does it include extra code or information that is not necessary?

4. Does the question describe any attempted solutions?


Then, using what you know about R and Python, try to debug the problem using the strategies in [the debugging chapter](https://srvanderplas.github.io/stat-computing-r-python/part-gen-prog/06-debugging.html). Once you are thoroughly stumped, or you believe you have solved the problem, compare your solutions to those given on StackOverflow using the link.

## Why Doesn't this R function work?

> I created the following function to append new strings on a vector of strings called "meals". However, when I use this function to append an string input into my "meals" vector, it does not work.

```
 add <- function(str) {
      meals <- append(meals, as.character(str))  
    }
```

[Link](https://stackoverflow.com/questions/39795961/why-doesnt-this-r-function-work?noredirect=1&lq=1) to original SO post. 


---

1. Are the question and problem description complete?

For the most part, they describe what they are trying to do and it is straightforward, but doesn't say how the code doesn't work if there is an error message. Is would be nice to include this information.

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

It says there is a problem but they don't really explain what the problem is. The code is reproducible, but the user would have to define a vector of strings that would work for the function to see what is wrong

3. Is the example minimal? Does it include extra code or information that is not necessary?

Yes, it is minimal. There doesn't appear to be extra code or information

4. Does the question describe any attempted solutions?

No they don't provide any attempted solutions 

```{R}
meals = c("soup","burger")

 add <- function(str) {
      meals = append(meals, as.character(str))  
      return(meals)
 }
 
add("chicken")
```
The function needed a return statement. This is also what was said in the post


## Function not working R

> I've never programmed before and am trying to learn. I'm following that "coursera" course that I've seen other people post about — a course offered by Johns Hopkins on R programming.

> Anyway, this was supposed to be my first function. Yet, it doesn't work! But when I type out all the steps individually, it runs just fine... Can anyone tell me why?

```
pollutantmean <- function(directory, pollutant, id = 1:332){
    x<- list.files("/Users/mike******/Desktop/directory", full.names=TRUE)
    y<- lapply(x, read.csv)
    z<- do.call(rbind.data.frame, y[id])

    mean(z$pollutant, na.rm=TRUE)
}
pollutantmean(specdata,nitrate,1:10)
[1] NA
Warning message:
In mean.default(z$pollutant, na.rm = TRUE) :
  argument is not numeric or logical: returning NA

####

x<- list.files("/Users/mike******/Desktop/specdata",full.names=TRUE)
y<- lapply(x,read.csv)
z<- do.call(rbind.data.frame,y[1:10])
mean(z$nitrate,na.rm=TRUE)
[1] 0.7976266
```


[Link](https://stackoverflow.com/questions/24123224/function-not-working-r/24141502)


---

1. Are the question and problem description complete?

Not really, it doesn't say what the code is trying to do. It is a simple function so it isn't hard to figure out though. The problem is more complete and it includes the error

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

There is a description of the problem but the code is not reproducible. The code loads in a data set from the users computer and that is not provided in the post. 

3. Is the example minimal? Does it include extra code or information that is not necessary?

There is some extra code that is not required for the problem. They complete the calculations outside of the function which is not really needed

4. Does the question describe any attempted solutions?

No attempted solutions other than doing the calculation without a function


Can't fully debug the code because the data set is not provided but based on what is provided and the stack overflow responses, the z$pollutant is not correct and should be changed. 


## Inexplicable error when trying to export my R notebook

> Getting this error from R Markdown when trying to export my .RMD

```
"Error in filter(Gastropods, Species == "Cellana") :  object 'Species' not found Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> filter"
```

> However, all my plots are coming out successfully. I can clearly see in the data that the species column is there and that Cellana is a species. No spelling errors or anything.

> My first 20 or so lines of code are below (between the ### symbols)


````{r echo=FALSE}
cat(paste(readLines("https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt"), collapse = '\n'))
````

You can find this sample file [here](https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt)


[Link](https://stackoverflow.com/questions/44193367/inexplicable-error-when-trying-to-export-my-r-notebook)

---

1. Are the question and problem description complete?

Yes, the question and problem description is complete. They describe where the problem occurs and when it happens with the error message. 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

The code is not reproducible because they are loading local files which are not provided

3. Is the example minimal? Does it include extra code or information that is not necessary?

The example is not minimal. There is a lot of extra code that makes it challenging to identify the specific problem

4. Does the question describe any attempted solutions?

There aren't really any attemped solutions


There is an error while trying to load dplyr and ggplot2 at the same time. Need to be loaded separately


## Python if elif else statement

> I'm trying to create a program with python that calculate the cost for shipping.

> However, I can't run the program to where it works properly.

> What ever my total is the same amount comes out as $6 for US and $8 for Canada. I can't seem to get pass that.

> Example:

```
total = raw_input('What is the total amount for your online shopping?')
country = raw_input('Shipping within the US or Canada?')

if country == "US":
    if total <= "50":
        print "Shipping Costs $6.00"
    elif total <= "100":
            print "Shipping Costs $9.00"
    elif total <= "150":
            print "Shipping Costs $12.00"
    else:
        print "FREE"

if country == "Canada":
    if total <= "50":
        print "Shipping Costs $8.00"
    elif total <= "100":
        print "Shipping Costs $12.00"
    elif total <= "150":
        print "Shipping Costs $15.00"
    else:
        print "FREE"
```


[Link](https://stackoverflow.com/questions/19371643/python-if-elif-else-statement)

---

1. Are the question and problem description complete?

Yes the problem is described pretty well in context of the code provided

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

No it is not reproducible. When I run the code I get errors, but they are different than the problem described in the post

3. Is the example minimal? Does it include extra code or information that is not necessary?

Yes, it is minimal. There isn't any extra code other than the single task they are attempting to complete

4. Does the question describe any attempted solutions?

There are not any other attempted solutions for the problem


```{python}
total = int(input('What is the total amount for your online shopping?'))
country = input('Shipping within the US or Canada?')

total =80 #manual inputs to check statments
country = "US"


if country == "US":
    if total <= 50:
        print("Shipping Costs $6.00")
    elif total <= 100:
            print("Shipping Costs $9.00")
    elif total <= 150:
            print("Shipping Costs $12.00")
    else:
        print("FREE")

if country == "Canada":
    if total <= 50:
        print("Shipping Costs $8.00")
    elif total <= 100:
        print("Shipping Costs $12.00")
    elif total <= 150:
        print("Shipping Costs $15.00")
    else:
        print("FREE")
```
There were a few errors in the code. raw_input() was not a defined function so I changed it to just input(). print statements were missing () and also the "total" variable should be compared to integers in the if statements rather than strings


# Professional Communication

## Slides

Create a set of quarto slides in the file slides.qmd. 

Set two different output formats - for instance, reveal.js and beamer. 

In your slides:

- Introduce yourself and show a picture of yourself
- Provide basic biographical information: birthday, where you grew up
- Show a picture of your favorite animal
- Provide your favorite plot, generated in either R or python. (This can be one you've generated in this class). Ensure that the code does not show, but the plot does.
- Provide a link to your CV, which you will generate in the next part.

## CV

Select a CV template that uses either LaTeX or Markdown:

- https://github.com/kazuyanagimoto/quarto-awesomecv-typst
- https://github.com/schochastics/quarto-cv
- https://www.overleaf.com/latex/templates/tagged/cv

Use the template to create a curriculum vitae that has your education, work experience, and any other sections you would like to include. Compile your CV and link to it in your slides. 
